DATA 621 - Business Analytics and Data Mining

### 2020-11-03 HW4/HW4_Draft.Rmd
Update using KNN with median 3 insted of mean 5

```{r dataClean}
# Clean up data values. Using setattr for fast data.table setting. Equivalent
# to levels(DT$X) <- c(a, b) but faster since changes by reference.
setattr(DT$MSTATUS, 'levels', c('Yes', 'No'))
setattr(DT$SEX, 'levels', c('M', 'F'))
setattr(DT$EDUCATION, 'levels', c('<High School', 'Bachelors', 'Masters', 'PhD',
                                  'High School'))
setattr(DT$JOB, 'levels', c('Unknown', 'Clerical', 'Doctor', 'Home Maker',
                            'Lawyer', 'Manager', 'Professional', 'Student',
                            'Blue Collar'))
setattr(DT$CAR_TYPE, 'levels', c('Minivan', 'Panel Truck', 'Pickup',
                                 'Sports Car', 'Van', 'SUV'))

@@

```{r model1RunFreq, cache = 2}
# preProcess with near-zero value and kNN imputation
trnXFDpp <- preProcess(trnXFD, method = c('nzv', 'knnImpute'), k = 5)

@@

```{r model1DummySev}
# Extract those observations with values > 0
trnSev <- trnX[TARGET_AMT > 0, TARGET_AMT]
# Set up dummy variables
trnDumSev <- dummyVars(TARGET_AMT ~ . + OWN * HOME_VAL + KIDSDRIV * HOMEKIDS +
                          HOME_VAL * INCOME * BLUEBOOK + CLM_FREQ * OLDCLAIM +
                          MSTATUS * SEX + CAR_USE * URBANICITY - INDEX -
                          TARGET_FLAG,
                        fullRank = TRUE, data = trnX[TARGET_AMT > 0])
# Create matrix of dummy values
trnXSD <- predict(trnDumSev, newdata = trnX[TARGET_AMT > 0])
# preProcess with near-zero value and kNN imputation
trnXSDpp <- preProcess(trnXSD, method = c('nzv', 'knnImpute'), k = 5)

@@

```{r validateM1F}
# Model 1 Frequency:: process validation data similar to training data
tstFreq <- factor(tstX$TARGET_FLAG, levels = c(0, 1),
                  labels = c("NoClaim", "Claim"))
tstDumFreq <- dummyVars(TARGET_FLAG ~ . + OWN * HOME_VAL + KIDSDRIV * HOMEKIDS +
                          HOME_VAL * INCOME * BLUEBOOK + CLM_FREQ * OLDCLAIM +
                          MSTATUS * SEX + CAR_USE * URBANICITY - INDEX -
                          TARGET_AMT,
                        fullRank = TRUE, data = tstX)
tstXFD <- predict(tstDumFreq, newdata = tstX)
tstXFDpp <- preProcess(tstXFD, method = c('nzv', 'knnImpute'))
tstXFDI <- predict(tstXFDpp, newdata = tstXFD)

@@

```{r validateM1S}
# Model 1 Severity: process validation data similar to training data
tstSev <- tstX[TARGET_AMT > 0, TARGET_AMT]
nobstst <- length(tstSev)
np <- summary(m1SevFit$finalModel)$df[3]
tstDumSev <- dummyVars(TARGET_AMT ~ . + OWN * HOME_VAL + KIDSDRIV * HOMEKIDS +
                          HOME_VAL * INCOME * BLUEBOOK + CLM_FREQ * OLDCLAIM +
                          MSTATUS * SEX + CAR_USE * URBANICITY - INDEX -
                          TARGET_FLAG,
                        fullRank = TRUE, data = tstX[TARGET_AMT > 0])
tstXSD <- predict(tstDumSev, newdata = tstX[TARGET_AMT > 0])
tstXSDpp <- preProcess(tstXSD, method = c('nzv', 'knnImpute'), k = 5)
tstXSDI <- predict(tstXSDpp, newdata = tstXSD)

>>>>

```{r dataClean}
# Clean up data values. Using setattr for fast data.table setting. Equivalent
# to levels(DT$X) <- c(a, b) but faster since changes by reference.
# Remove spaces where possible too
setattr(DT$MSTATUS, 'levels', c('Yes', 'No'))
setattr(DT$SEX, 'levels', c('M', 'F'))
setattr(DT$EDUCATION, 'levels', c('<HighSchool', 'Bachelors', 'Masters', 'PhD',
                                  'HighSchool'))
setattr(DT$JOB, 'levels', c('Unknown', 'Clerical', 'Doctor', 'HomeMaker',
                            'Lawyer', 'Manager', 'Professional', 'Student',
                            'BlueCollar'))
setattr(DT$CAR_TYPE, 'levels', c('Minivan', 'PanelTruck', 'Pickup',
                                 'SportsCar', 'Van', 'SUV'))

@@

```{r model1RunFreq, cache=TRUE}
# preProcess with near-zero value and kNN imputation
trnXFDpp <- preProcess(trnXFD, method = c('nzv', 'knnImpute'),
                       k = 3, knnSummary = median)

@@

```{r model1DummySev}
# Extract those observations with values > 0
trnSev <- trnX[TARGET_AMT > 0, TARGET_AMT]
# Set up dummy variables
trnDumSev <- dummyVars(TARGET_AMT ~ . + OWN * HOME_VAL + KIDSDRIV * HOMEKIDS +
                          HOME_VAL * INCOME * BLUEBOOK + CLM_FREQ * OLDCLAIM +
                          MSTATUS * SEX + CAR_USE * URBANICITY - INDEX -
                          TARGET_FLAG,
                        fullRank = TRUE, data = trnX[TARGET_AMT > 0])
# Create matrix of dummy values
trnXSD <- predict(trnDumSev, newdata = trnX[TARGET_AMT > 0])
# preProcess with near-zero value and kNN imputation
trnXSDpp <- preProcess(trnXSD, method = c('nzv', 'knnImpute'),
                       k = 3, knnSummary = median)

@@

```{r validateM1F}
# Model 1 Frequency:: process validation data similar to training data
tstFreq <- factor(tstX$TARGET_FLAG, levels = c(0, 1),
                  labels = c("NoClaim", "Claim"))
tstDumFreq <- dummyVars(TARGET_FLAG ~ . + OWN * HOME_VAL + KIDSDRIV * HOMEKIDS +
                          HOME_VAL * INCOME * BLUEBOOK + CLM_FREQ * OLDCLAIM +
                          MSTATUS * SEX + CAR_USE * URBANICITY - INDEX -
                          TARGET_AMT,
                        fullRank = TRUE, data = tstX)
tstXFD <- predict(tstDumFreq, newdata = tstX)
tstXFDpp <- preProcess(tstXFD, method = c('nzv', 'knnImpute'),
                       k = 3, knnSummary = median)
tstXFDI <- predict(tstXFDpp, newdata = tstXFD)

@@

```{r validateM1S}
# Model 1 Severity: process validation data similar to training data
tstSev <- tstX[TARGET_AMT > 0, TARGET_AMT]
nobstst <- length(tstSev)
np <- summary(m1SevFit$finalModel)$df[3]
tstDumSev <- dummyVars(TARGET_AMT ~ . + OWN * HOME_VAL + KIDSDRIV * HOMEKIDS +
                          HOME_VAL * INCOME * BLUEBOOK + CLM_FREQ * OLDCLAIM +
                          MSTATUS * SEX + CAR_USE * URBANICITY - INDEX -
                          TARGET_FLAG,
                        fullRank = TRUE, data = tstX[TARGET_AMT > 0])
tstXSD <- predict(tstDumSev, newdata = tstX[TARGET_AMT > 0])
tstXSDpp <- preProcess(tstXSD, method = c('nzv', 'knnImpute'),
                       k = 3, knnSummary = median)
tstXSDI <- predict(tstXSDpp, newdata = tstXSD)
